Analysis of the included studies

### 2023-05-15 analyses/scripts/full_data_extraction_citation_table.Rmd
Now using the here package to manage paths

```{r}
#' load packages
library("tidyverse")
library("scales")
library("conflicted")
library("knitr")

@@

```{r}
#create a folder for storing the manuscript figures

if (!dir.exists("../figs_manuscript")) {
  dir.create("../figs_manuscript",
    showWarnings = TRUE
  )
}

#save figures in this folder
save_fig_here <- '../figs_manuscript'
```

```{r}
# Load the cleaned data 
long_data <- read_rds('../data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')
```

```{r}
# Load the data with citations
compact_data_with_citation_keys_init <- read_rds("../data/compact_data_with_citation_keys_cleaned.rds")

# Clean various variables
compact_data_with_citation_keys <- compact_data_with_citation_keys_init %>%
  mutate(vax_modelled = ifelse(str_detect(intervention_modelled, "vaccination"),
    "yes",
    "no"
  ), 
  intervention_type = case_when(
    vax_modelled == "no" & vax_modelled_with_non_vax == "no" ~ "no_vax", # Vaccination was not modelled
    vax_modelled == "yes" & vax_modelled_with_non_vax == "no" ~ "vax_combination_with_others", # when vax was modelled but not for comparison as a single intervention
    vax_modelled == "yes" & vax_modelled_with_non_vax == "yes" ~ "vax_single", # when vax was modelled as a single intervention
  ),
    publication_year = as.numeric(publication_year),
    author_in_country_studied = as.character(author_in_country_studied)
  ) %>%
  arrange(publication_year) %>%
  mutate(
    author_affiliation_type = str_replace_all(author_affiliation_type, " ", " + "),
    author_in_country_studied = if_else(author_in_country_studied == "NA", "not_applicable",
      author_in_country_studied
    ),
    year_aggreg = as.numeric(ifelse(publication_year < 2006, # An approach to aggregate the years before 2006 into one group because of the low number of papers
      2005,
      publication_year
    )),
    collab_type = as_factor(if_else(author_affiliation_type == "academic_institutions",
      "purely_academic",
      "mixed"
    ))
  )
```

```{r}
# Data dictionaries

# parametrization description dictionary
parametrization_str_replacements <- c(
  "values_from_literature" = "literature",
  "values_from_guess_and_expert_opion" = "expert_opinion",
  "values_fitted_to_ts" = "fitted",
  " " = " and " # replace space with 'and' to make it more readable
)

# validation description dictionary
validation_str_replacements <- c(
  "compared_with_data" = "data",
  "compared_with_other_model_output" = "another_model",
  "model_not_validated" = "none",
  " " = "_and_"
)

# Clean the parametrization and validation variables with dictionary
compact_data_with_citation_keys <- compact_data_with_citation_keys %>%
  mutate(parametrization = str_replace_all(
    parametrization,
    parametrization_str_replacements
  )) %>%
  mutate(validation = str_replace_all(
    validation,
    validation_str_replacements
  )) %>%
  mutate(model_structure = str_replace(model_structure, 
                                       "deterministic stochastic", 
                                       "both"
                                       )
         )
```

>>>>

```{r}
#' load packages
suppressPackageStartupMessages({
  library("tidyverse")
  library("scales")
  library("conflicted")
  library("knitr")
  library("here")
  library("kableExtra")
  })

@@

```{r}
here::i_am("analyses/scripts/full_data_extraction_citation_table.Rmd")
#I/O paths
figs_dir <- "analyses/figs"
data_dir <- "analyses/data"
scripts_dir <- "analyses/scripts"

# Create a folder for storing the figures

if (!dir.exists(here::here(figs_dir))) {
  dir.create(here::here(figs_dir),
    showWarnings = TRUE
  )
}
```

```{r load_data}
#' re-run the data cleaning step, in case something has changed 
#' TO DO: Use GNU make for this

source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))

# The data with citations 
compact_data_with_citation_keys <- read_rds(
  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'
  ))
```

### 2023-05-15 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Now using the here package to manage paths

```{r}
#' load packages
library('tidyverse')
library('ggthemes')
library('scales')
library('janitor')
library('countrycode')
library('bib2df')
library('conflicted')
library('ggwordcloud')

@@

```{r}
#directories
# Figures
figs_dir <- "../figs_manuscript"

# Create a folder for storing the manuscript figures if it doesn't exist
if (!dir.exists('../figs_manuscript'))
    {
    dir.create('../figs_manuscript', 
               showWarnings = FALSE)
    }

data_dir <- "../data"
```

@@

source("./orv_models_review_data_cleaning.R")

# Load the cleaned data 
long_data <- read_rds(file.path(data_dir, "review_data_long_cleaned.rds"))

#The cleaned data without citations
compact_data_init <- read_rds(
  file.path(data_dir, "review_data_compact_cleaned.rds")
  )

# The data with citations 
compact_data_with_citation_keys <- read_rds(
  '../data/compact_data_with_citation_keys_cleaned.rds'
  )

>>>>

```{r}
#' load packages
suppressPackageStartupMessages({
  library('tidyverse')
  library('ggthemes')
  library('scales')
  library('janitor')
  library('countrycode')
  library('bib2df')
  library('conflicted')
  library('ggwordcloud')
  library('here')
  })

@@

```{r}
#I/O directories
figs_dir <- "analyses/figs"
data_dir <- "analyses/data"
scripts_dir <- "analyses/scripts"

here::i_am("analyses/scripts/orv_sys_rev_data_analysis.Rmd")
# Create a folder for storing the figures

if (!dir.exists(here::here(figs_dir))) {
  dir.create(here::here(figs_dir),
    showWarnings = TRUE
  )
}
```

@@

source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))

# Load the cleaned data 
long_data <- read_rds(here::here(data_dir, "review_data_long_cleaned.rds"))

#The cleaned data without citations
compact_data_init <- read_rds(
  here::here(data_dir, "review_data_compact_cleaned.rds")
  )

# The data with citations 
compact_data_with_citation_keys <- read_rds(
  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'))
